\vspace{-2cm} Content of Municipal Government Websites

### 2017-03-24 paper/manuscript.tex
commented on content change
minor update

Alternatively, the more commonplace LDA is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes. As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''. Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership. In a way, this captures the data-generating process more closely.

@@

@@

>>>>

Alternatively, the more commonplace LDA \cite{Blei2003} is another feasible way of modeling the way in which websites receive a makeover when party control of the mayorship changes. As noted by \citep{Rosen-Zvi2004}, LDA can be considered a special case of the author-topic model, ''where each document has one unique author''. Here, a city website would be a collection of documents, each of which originates entirely from either Democratic or Republican leadership. In a way, this captures the data-generating process more closely.

@@

There is also a possibility that city size is a determinant of the number of topics. Larger cities tend to have bigger websites, owing to a larger set of issues that need to be dealt with.

@@

% latex table generated in R 3.3.2 by xtable 1.8-2 package
% Fri Mar 24 12:21:19 2017
\begin{table}[ht]
\centering
\begin{tabular}{lrrrr}
  \hline
File type & oct15 & jan16 & feb16 & mar16 \\ 
  \hline
.pdf & 358 & 183 & 111 & 394 \\ 
  .aspx &  99 & 112 & 116 &  76 \\ 
  .jpg &  22 &  24 &  17 &  12 \\ 
  .gif &   3 &   5 &   1 &   5 \\ 
  .JPG &   3 &   2 &   1 &   5 \\ 
  .png &   3 &   7 &   2 &   1 \\ 
  .asmx &   2 &   1 &   1 &   5 \\ 
  .PDF &   1 &   1 &   1 &   2 \\ 
   \hline
\end{tabular}
\caption{File types of Indy.gov at different points in time} 
\end{table}
